Global patterns of forest autotrophic carbon fluxes

### 2020-02-13 manuscript/manuscript draft.Rmd
table 1 adjustment
Update manuscript draft.Rmd

**Climate is a significant driver of FACF across broad spatial scales** [@cleveland_relationships_2011]. The majority of studies have focused on exploring the relationships of FACF to mean annual temperature (MAT) and mean annual precipitation (MAP), as the most commonly reported site-level climate variables. These variables have the advantage that they describe broad trends in temperature and water availability, and therefore capture a lot of global-scale variation in climate. There is strong evidence that both MAT and MAP show significant positive relationships with FACF [@chu_does_2016]. However, as with latitude, the shape of those relationships is not always clear, and, again, is complicated by the use of different measures of FACF across studies. Various measures of primary productivity {**FACF?**} saturate at high levels of MAP, though the saturation points identified vary from 1500mm [@luyssaert_co_2007] up to 2445mm MAP [@schuur_productivity_2003]. Studies of the influence of MAT on productivity {**FACF?**} are less conclusive. Luyssaert et al. [-@luyssaert_co_2007] examined GPP and NPP and found that, while GPP increases linearly with MAT, NPP saturates at around 10$^\circ$C MAT. In contrast, Larjavaara and Muller-Landau [-@larjavaara_temperature_2012], find that increases in GPP saturate at approximately 25$^\circ$C MAT, while Schuur [-@schuur_productivity_2003] shows that NPP increases linearly with temperature. bbl:maybe remove following sentences The influence of these climate variables on productivity is further complicated by the possibility of interactive effects occurring between them. Taylor et al. [-@taylor_temperature_2017] showed that increased MAP had a negative effect at low MAT, but a positive effect at high levels of MAT, and *vice versa* {**Helene found this confusing**}, suggesting that both temperature and water availability are important in explaining productivity.  {**It would be good to add some more citations on soil respiraiton. I'm sure BBL can help.**}

@@

*We found no evidence that allocation between fluxes varied substantially with latitude or climate. There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.* **THIS HAS CHANGED: [issue #51](https://github.com/forc-db/Global_Productivity/issues/51#issuecomment-581892186)

>>>>

**Climate is a significant driver of FACF across broad spatial scales** [@cleveland_relationships_2011]. The majority of studies have focused on exploring the relationships of FACF to mean annual temperature (MAT) and mean annual precipitation (MAP), as the most commonly reported site-level climate variables. These variables have the advantage that they describe broad trends in temperature and water availability, and therefore capture a lot of global-scale variation in climate. There is strong evidence that both MAT and MAP show significant positive relationships with FACF [@chu_does_2016]. However, as with latitude, the shape of those relationships is not always clear, and, again, is complicated by the use of different measures of FACF across studies. Various measures of primary productivity {**FACF?**} saturate at high levels of MAP, though the saturation points identified vary from 1500mm [@luyssaert_co_2007] up to 2445mm MAP [@schuur_productivity_2003]. Studies of the influence of MAT on productivity {**FACF?**} are less conclusive. Luyssaert et al. [-@luyssaert_co_2007] examined GPP and NPP and found that, while GPP increases linearly with MAT, NPP saturates at around 10$^\circ$C MAT. In contrast, Larjavaara and Muller-Landau [-@larjavaara_temperature_2012], find that increases in GPP saturate at approximately 25$^\circ$C MAT, while Schuur [-@schuur_productivity_2003] shows that NPP increases linearly with temperature. bbl:maybe remove following sentences The influence of these climate variables on productivity is further complicated by the possibility of interactive effects occurring between them. Taylor et al. [-@taylor_temperature_2017] showed that high rainfall had a negative effect on productivity where MAT was low, but a positive effect at sites with high MAT. Similarly, at sites with high MAT, increases in rainfall were found to enhance productivity, in contrast to cooler sites, where high levels of rainfall inhibit productivity.  {**It would be good to add some more citations on soil respiraiton. I'm sure BBL can help.**}

@@

We found no evidence that allocation between fluxes varied substantially with latitude or climate. There were no significant results from regressing ratios of carbon fluxes against latitude, or against any of the climate variables.
